The ChEMBL database as Linked Open Data

### 2012-03-05 article.tex
Added a basic, draft introduction

Linked Data, pharmaceutical research, Open PHACTS, ...

This data set has been previously used in~\cite{Willighagen2011} and in Foo where the data is used
in the Foo framework (book chapter...)

>>>>

Despite the data deluge, finding new, unique, but significant patterns explaining biological
phenomena not yet understood is limited by the availability of data. Such data analysis is
beyond the scope is single data sets; it requires data integration from many sources, for
example, systems biology integrating micro-array differential expression to biological
pathways~\cite{}. Another prominent example is drug discovery where a new unique chemical entity is
searched with just the right biological properties. This too requires linking many
data sets~\cite{Samwald2011,OpenPHACTS}.

ChEMBL contains biological activities for over a million chemical entities, extracted from
literature, providing a unique resource for drug discovers~\cite{Warr2010}. Originally, this
data was available for download and via a web interface. The former requires setting up
the data in a relational database, while the latter limits the machine access to the data.
Two independent teams created RDF triples for the ChEMBL data, resulting in exposure
via Chem2Bio2RDF~\cite{} and ChEMBL-RDF~\cite{Willighagen2011}.

This paper presents the history of the ChEMBL-RDF data set, details of the latest structures
and ontologies used for the RDF version of ChEMBL 13, and a few new example use cases,
exemplifying how the data set can be linked to other data sources to further support
research in the life sciences.
